An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-23 paper/paper.tex
Paper: rought draft of acknowledgements

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
Acknowledgements
\end{abstract}

>>>>

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
% TODO adjectives
% TODO format this section better
Mih\'aly H\'eder, our on-site Project Advisor, for his advice, insight, expertise, and bottomless tea kettle.\\

\noindent G\'abor S\'ark\"ozy, our off-site Project Advisor, for his guidance, encouragement, and editorial skills. \\

\noindent Worcester Polytechnic Institute, for the opportunity to study abroad. \\

\noindent MTA SZTAKI, for the resources to design, develop, and test our system. \\

\noindent The employees of MTA SZTAKI, for their open arms and continued friendship.
\end{abstract}
